---
title: "Sample R markdown document"
author: "LakshmiPrasanna. Thsaliki"
date: "04/12/2020"
output: word_document
---

In this document I will show how to execute basic statistical analysis on IRIS dataset. The main aim of this document is to get a free flow of using R markdown to create analysis

I have read quite few articles about the convenience  of using R markdown for Document creation.
Although, I am still learning a lot about the markdown shorcuts and snippets that becomes handy in creating interesting document, I will showcase few formatting ways of using the R markdown


This document is my analysis on the data set: IRIS Dataset.
The following are the aspects I have explored

•	Data Summary

•	plotting

•	Visualizing Distribution Of Data

PREPROCESSING
Step 1 Loading the data and necessary libraries:
```{r}
rm(list=ls())
data(iris())
dim(iris)
```

This data has 150 rows and 5 columns.

```{r}
summary(iris)
```

__There are 50 Setosa, 50 Versicolor and 50 Virginica specis in this dataset__


```{r}
plot(iris$Petal.Length, iris$Petal.Width)
```
_Plot of Length and width of IRIS petals_


```{r}
hist(iris$Petal.Length)
```

__The Histogram shows the distribution that the petal length is 1 for most of the values__

This is my small presentation of the R markdown. 

Thank you for going through








